### 2017-02-24 MSSM/MSSM.tex
More editing, plus additional cosmetic fixes from quick skim

Single-top and \ttbar background samples are generated using \texttt{POWHEG},
with \texttt{MadGraph5\_aMC@NLO} \cite{amcnlo} used for the generation of di-boson background
samples. %and part of the W+$\gamma$ background, which is included in the \emu channel only.
\Wjets and \Zll backgrounds are generated with the \texttt{MadGraph 5} \cite{madgraph}
matrix element generator. Samples containing both a mixture
of jet multiplicities (`inclusive' samples) and samples with one, two, three or four jets (`exclusive' samples)
are generated. These exclusive samples increase the available number of
background events with higher jet multiplicities. %note LO samples used because to get same number of effective
%events would need to generate more NLO samples
The `inclusive' and `exclusive' samples are reweighted
before they are combined so as to preserve the correct
fractions of events with each jet multiplicity. The $\PW+\Pphoton$ background samples,
only included in the \emu channel, are generated either with \texttt{MadGraph 5} or 
with \texttt{MadGraph5\_aMC@NLO}.

@@

A topological selection on the \mT~variable, 
introduced in section \ref{sec:hhh_selection_categories}, is made on 
events in the \mutau channel. This selection and the
choice of hadronic tau isolation working point provide two competing
effects and therefore they are optimised simultaneously.
The ``pre-fit'' expected upper limits, determined without the fit
to the real observed data, on \xsbr for both $\Pgluon\Pgluon\phi$ and $\Pbottom\Pbottom\phi$
production with decay into $\Pgt\Pgt$ at several mass points 
in the $90\,\GeV$--$3.2\,\TeV$ range are used as a figure of merit.
Because of the use of such a wide range of signal masses, it
is not possible to choose a selection that is optimal
for every mass point. This is illustrated in figure \ref{fig:mssm_selection_mt_taumt}:
figure \ref{fig:mssm_selection_mt_taumt}a shows the upper limit on \xsbr for
the gluon fusion production process, for a mass $m_{\phi} = 160\,\GeV$, with
figure \ref{fig:mssm_selection_mt_taumt}b showing this upper limit for $m_{\phi} = 2.9\,\TeV$.
Figure \ref{fig:mssm_gradcuts_mt} shows the effect of gradually loosening the \mT~and hadronic
tau isolation working point selections on both the \Pgluon\Pgluon$\phi$ and \Pbottom\Pbottom$\phi$ production processes.

@@

In summary, the two categories are defined as:
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item \textbf{No b-tag}: No b-tagged jets. This category targets the $\Pg\Pg\phi$ production mode but is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal.
\item \textbf{b-Tag}: At least one b-tagged jet, at most one 
jet with $\pTm>30\,\GeV$. This second requirement, the jet veto, reduces the \ttbar background. 
Due to the lower \pT~requirement considered for
b-tagging compared with the requirement for the jet veto, it is still possible for there
to be more than one b-tagged jet in the event.
\end{itemize}

@@

The method described so far works well in the no b-tag categories, but in the b-tag category of both channels
the \ttbar background dominates. This is illustrated in figure \ref{fig:bkgs_highmtctrl}, where
the high-\mT~region in the no b-tag category, figure \ref{fig:bkgs_highmtctrl}a, is compared with the high-\mT~region in the 
b-tag category, figure \ref{fig:bkgs_highmtctrl}b, of the \etau channel. It is clear that the \ttbar 
background is much larger than the \Wjets background in the b-tag high-\mT~control region.
For this reason the estimate of the number
of \Wjets events in this category is made with a relaxed category selection where the b-tagging
requirement itself is removed, but the jet requirements remain. Events with at least one 
jet with $\pTm>20\,\GeV$ and with $|\eta|<2.4$, but at most one jet with $\pTm>30\,\GeV$ and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
region is determined by the estimate given by the number of \Wjets events
estimated in this one-jet selection, multiplied by an extrapolation factor 
$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{\text{T}},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{one-jet selection}}}$.
\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_10_shapes_postfit.pdf}}
\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_13_shapes_postfit.pdf}}
\end{center}
\caption[High-\mT~control region in the no b-tag and b-tag
categories of the \etau channel.]{High-\mT~control region in the (a) no b-tag and (b) b-tag categories of the \etau
channel. In the no b-tag category the \Wjets background, drawn together with the small
 di-boson plus single-top backgrounds as the `electroweak' background component, dominates. In the b-tag
category the \ttbar background is larger than the \Wjets background.}
\label{fig:bkgs_highmtctrl}
\end{figure}

@@

The uncertainty on the luminosity measurement amounts to 6.2\% for

@@

using \ac{MC} samples.

@@

The combined uncertainty on the electron and muon identification, isolation, and
trigger efficiencies amounts to 2\% \cite{CMS-PAS-HIG-16-037}. For hadronic taus the identification and
isolation uncertainty amounts to 6\% in the \etau and \mutau channels
and 12\% in the \tautau channel, with an additional 7\% uncertainty
on the tau trigger efficiency added in quadrature for that channel \cite{CMS-PAS-HIG-16-037}. This
uncertainty is split between a part that is correlated between the channels, 

@@

The uncertainties on lepton/hadronic tau identificiation, isolation and 

@@

is estimated using \ac{MC} samples.

@@

The uncertainty on the $\text{jet}\rightarrow\Pgth$ fake rate

@@

to those backgrounds where the normalisation is estimated from \ac{MC} and
where the hadronic taus are mimicked by jets, that is the \Zellell background

@@

\subsubsection*{$\Pe\rightarrow\Pgth$ and $\Pgm\rightarrow\Pgth$ fake rate}
The $\Pe\rightarrow\Pgth$ fake rate uncertainty ranges from $10$--$30$\%,

@@

applied to the \Zellell background with the hadronic tau faked by an electron.
The $\Pgm\rightarrow\Pgth$ fake rate uncertainty ranges from $20$--$30$\%, depending
on the anti-muon discriminator used\cite{CMS-PAS-HIG-16-037}. This uncertainty is applied to the \Zellell
background with the hadronic tau faked by a muon.

@@

The uncertainties on the jet energy corrections are applied
by shifting the jet energy up and down by the \pT-and $\eta$-dependendent

@@

each category. Where the change in normalisation is non-negligible the
uncertainty is applied. It ranges from $1$--$10$\% depending on process and category.

@@

Uncertainties on the b-tagging efficiency and light jet mis-tagging
rates are given as a function of jet \pT-and $\eta$-for the 

@@

The b-tagging scale factors are are varied within these uncertainties

@@

evaluated. If the change in normalisation is non-negligible this
uncertainty is applied. The uncertainty varies from $1$--$5$\%.

@@

Uncertainties on the \MET~resolution and response are estimated

@@

uncertainty and evaluating the effect on process

@@

the Drell-Yan cross section is not applied as an uncertainty. In the no b-tag (b-tag) category a 3\% (5\%)
extrapolation uncertainty from \Zmm to \Ztautau is applied \cite{CMS-PAS-HIG-16-037}.
\item \Zellell: The uncertainty on the Drell-Yan cross-section
is to 4\% \cite{CMS-PAS-HIG-16-037}.
\item \ttbar: The uncertainty on the \ttbar production cross-section amounts
to 6\% \cite{CMS-PAS-HIG-16-037}.
\item di-boson and single-top: The combined uncertainty on the di-boson and
single-top production cross sections amounts to 5\% \cite{CMS-PAS-HIG-16-037}.

@@

on the observed data and subtracted backgrounds in the control regions are taken into account by

@@

uncertainty on $R_{W}^{\text{OS/SS}}$ amounts to 2\% in the no b-tag

@@

category of the \mutau (\etau) channel. The systematic uncertainty on

@@

The statistical uncertainty on the low \mT/high \mT~ratio is 2\% in the no b-tag

@@

The systematic uncertainty on this ratio amounts to 20\%. As the \Wjets background
in the \tautau and \emu channels is estimated from \ac{MC} a 4\% theoretical
production cross-section uncertainty is applied.
\item QCD: In the \emu channel the uncertainty on the QCD estimate

@@

\tautau channel the statistical uncertainty on the QCD estimate is derived from

@@

category and 20\% in the b-tag category. An additional systematic uncertainty on the

@@

uncertainties on the observation and subtracted \ac{MC} backgrounds in the control
region used to derive the QCD estimate is accounted for by the inclusion of these control
regions in the fit. The uncertainty on the opposite-sign to same-sign ratio, based on

@@

uncertainties on the SM and MSSM Higgs cross section predictions are taken into account.

@@

\subsection{Shape uncertainties}
\label{sec:mssm_uncs_shape}
\subsubsection*{$\Pgt_{h}$ energy scale}
The energy of hadronic taus is varied up and down by 3\% \cite{CMS-PAS-HIG-16-037}, affecting
the shape of the total transverse mass distribution.
The uncertainty is applied to the signal samples and to
backgrounds containing real hadronic taus in the \etau, \mutau, and \tautau channels, namely
\Ztautau, and the components of the \ttbar and single-top+di-boson background with real 
hadronic taus.
\subsubsection*{Electron energy scale}
The energy of electrons is varied by 1\% in the barrel and by 2.5\% in the endcaps \cite{CMS-PAS-HIG-16-037}. This 
uncertainty is applied to the
signals and to the \Ztautau background in the \emu channel.
\subsubsection*{High-\pT~$\Pgth$ ID efficiency}
An additional $\Pgth$ identification uncertainty of $\frac{20\% \times p_{\text{T}}}{\TeV}$
is applied to account for the extrapolation from the tau ID efficiency
measurement, which uses mostly taus close to the \PZ peak, to taus with higher transverse momenta \cite{CMS-PAS-HIG-16-037}. This
uncertainty is applied to signal and backgrounds with real taus in the \etau, \mutau and \tautau channels.
The shape difference between the nominal, up- and down- shapes for this uncertainty in the no b-tag category
of the \tautau channel can be seen for a high-mass signal sample in figure \ref{fig:mssm_highpttauid_shapes}a and
for the \Ztautau background in figure \ref{fig:mssm_highpttauid_shapes}b. Because the \Ztautau background
has much softer hadronic taus than the high-mass signal sample, the impact of this uncertainty on the shape
is much smaller.
\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$ signal at $m_{\phi} = 3.2\,\TeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/highpT_tauID_comp_tt_nobtag_ggh3200.pdf}}
\subfloat[\Ztautau background]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/highpT_tauID_comp_tt_nobtag_ZTT.pdf}}
\end{center}
\caption[Impact of the high-\pT~tau ID uncertainty in the no b-tag category
of the \tautau channel for a high-mass signal sample and the \Ztautau
background.]{Impact of the high-\pT~tau ID uncertainty in the no b-tag category of the
\tautau channel for (a) a high-mass signal sample and (b) the \Ztautau background. The effect on the shape is much
larger in the high-mass signal sample, which contains hadronically decaying taus with much higher
\pT~than the \Ztautau sample.}
\label{fig:mssm_highpttauid_shapes}
\end{figure}
\subsubsection*{Top quark \pT~reweighting}
To account for the uncertainty in the derivation of the top-quark \pT~reweighting, a shape
uncertainty is applied to the \ttbar background. This uncertainty amounts to a 100\% variation
of the correction, that is the difference between applying the correction twice and not applying the correction at all.
\subsubsection*{Drell-Yan shape reweighting}
An uncertainty on the Drell-Yan shape reweighting based on \Zmm events
is applied as 100\% of the correction to the \Ztautau background \cite{CMS-PAS-HIG-16-037}. 
\subsubsection*{Jet$\rightarrow\Pgt_{h}$ fake rate shape reweighting}
On the \Wjets background in the \etau and \mutau channels a shape 
uncertainty of $\frac{-20\% \times p_{\text{T}}}{\GeV}$ is 
applied. This uncertainty is derived from variations in the data/\ac{MC} ratio
for the $\text{jet}\rightarrow\Pgth$ fake rate as a function of jet \pT~in 
\Wjets events \cite{CMS-PAS-HIG-16-037}.

@@

\subsection{Inclusion of control regions in the fit}
\label{sec:mssm_sigext_ctrl}
The control regions used for estimation of the 
\Wjets and QCD background contributions in the signal regions, discussed
in section \ref{sec:mssm_bkgs_etmt_ctrl}, are included in the fit. They
are added to the likelihood as single-bin counting experiments. In a given
category of one of the channels, the \Wjets
normalisation is fully correlated between the three control 
regions and the signal region. One common, freely floating, nuisance parameter
controls the \Wjets normalisation in all four regions. The QCD normalisation
is fully correlated between the opposite-sign and same-sign low-\mT~regions. The
same is true for the opposite-sign and same-sign high-\mT~regions. This means there are
two freely floating nuisance parameters that govern the QCD normalisation: one
that controls the QCD normalisation in the two low-\mT~regions, and one
that controls it in the two high-\mT~regions.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-a.pdf}}
\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-b.pdf}}
\end{center}
\caption[Distributions of \mTtot~in the no b-tag and b-tag categories
of the \mutau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
of the \mutau channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid. Note that, to incorporate
the observed Higgs boson at $125\,\GeV$, the $m_{\PHiggslight}^{mod+}$ scenario includes a \PHiggslight boson
at around $125\,\GeV$ with a much larger \xsbr than the $1\,\TeV$ \PHiggs and \PHiggsps, and this is
the reason for the doubly-peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_results_mttot_mt}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-a.pdf}}
\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-b.pdf}}
\end{center}
\caption[Distributions of \mTtot~inthe no b-tag and b-tag 
categories of the \etau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
of the \etau channel. The signal of the three neutral Higgs bosons at \mA~=$1\,\TeV$
and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_results_mttot_et}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-a.pdf}}
\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-b.pdf}}
\end{center}
\caption[Distributions of \mTtot~in the no b-tag and b-tag categories
of the \tautau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
of the \tautau channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_results_mttot_tt}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-a.pdf}}
\subfloat[b-Tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_007-b.pdf}}
\end{center}
\caption[Distributions of \mTtot~in the no b-tag and b-tag categories of 
the \emu channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
of the \emu channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
and \tanb~$=50$ in the $m_{\PHiggslight}^{mod+}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_results_mttot_em}
\end{figure}

>>>>

Single-top and \ttbar background samples are generated using \texttt{POWHEG},
with \texttt{MadGraph5\_aMC@NLO} \cite{amcnlo} used for the generation of di-boson background
samples. %and part of the W+$\gamma$ background, which is included in the \emu channel only.
\Wjets and \Zll backgrounds are generated with the \texttt{MadGraph 5} \cite{madgraph}
matrix element generator. Samples containing both a mixture
of jet multiplicities (`inclusive' samples) and samples with one, two, three or four jets (`exclusive' samples)
are generated. These exclusive samples increase the available number of
background events with higher jet multiplicities. %note LO samples used because to get same number of effective
%events would need to generate more NLO samples
The `inclusive' and `exclusive' samples are reweighted
before they are combined so as to preserve the correct
fractions of events with each jet multiplicity. The $\PW{+}\Pphoton$ background samples,
only included in the \emu channel, are generated either with \texttt{MadGraph 5} or 
with \texttt{MadGraph5\_aMC@NLO}.

@@

A topological selection on the \mT~variable, 
introduced in section \ref{sec:hhh_selection_categories}, is made on 
events in the \mutau channel. This selection and the
choice of hadronic tau isolation working point provide two competing
effects and therefore they are optimised simultaneously.
The ``pre-fit'' expected upper limits, determined without the fit
to the real observed data, on \xsbr for both $\Pgluon\Pgluon\phi$ and $\Pbottom\Pbottom\phi$
production with decay into $\Pgt\Pgt$ at several mass points 
in the $90\,\GeV$--$3.2\,\TeV$ range are used as a figure of merit.
Because of the use of such a wide range of signal masses, it
is not possible to choose a selection that is optimal
for every mass point. This is illustrated in figure \ref{fig:mssm_selection_mt_taumt}:
figure \ref{fig:mssm_selection_mt_taumt}a shows the upper limit on \xsbr for
the gluon fusion production process, for a mass $m_{\phi} = 160\,\GeV$, with
figure \ref{fig:mssm_selection_mt_taumt}b showing this upper limit for $m_{\phi} = 2.9\,\TeV$.
Figure \ref{fig:mssm_gradcuts_mt} shows the effect of gradually loosening the \mT~and hadronic
tau isolation working point selections on both the $\Pgluon\Pgluon\phi$ and $\Pbottom\Pbottom\phi$ production processes.

@@

In summary, the two categories are defined as:
\begin{itemize}
\setlength{\itemsep}{-\baselineskip}
\item \textbf{No b-tag}: No b-tagged jets. This category targets the $\Pg\Pg\phi$ production mode but is also sensitive to some of the $\Pbottom\Pbottom\phi$ signal.
\item \textbf{B-tag}: At least one b-tagged jet, at most one 
jet with $\pTm>30\,\GeV$. This second requirement, the jet veto, reduces the \ttbar background. 
Due to the lower \pT~requirement considered for
b-tagging compared with the requirement for the jet veto, it is still possible for there
to be more than one b-tagged jet in the event.
\end{itemize}

@@

The method described so far works well in the no b-tag categories, but in the b-tag category of both channels
the \ttbar background dominates. This is illustrated in figure \ref{fig:bkgs_highmtctrl}, where
the high-\mT~region in the no b-tag category, figure \ref{fig:bkgs_highmtctrl}a, is compared with the high-\mT~region in the 
b-tag category, figure \ref{fig:bkgs_highmtctrl}b, of the \etau channel. It is clear that the \ttbar 
background is much larger than the \Wjets background in the b-tag high-\mT~control region.
For this reason the estimate of the number
of \Wjets events in this category is made with a relaxed category selection where the b-tagging
requirement itself is removed, but the jet requirements remain. Events with at least one 
jet with $\pTm>20\,\GeV$ and with $|\eta|<2.4$, but at most one jet with $\pTm>30\,\GeV$ and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
region is determined by the estimate given by the number of \Wjets events
estimated in this one-jet selection, multiplied by an extrapolation factor 
$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{\text{T}},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{one-jet selection}}}$.
\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_10_shapes_postfit.pdf}}
\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_13_shapes_postfit.pdf}}
\end{center}
\caption[High-\mT~control region in the no b-tag and b-tag
categories of the \etau channel.]{High-\mT~control region in the (a) no b-tag and (b) b-tag categories of the \etau
channel. In the no b-tag category the \Wjets background, drawn together with the small
 di-boson plus single-top backgrounds as the `electroweak' background component, dominates. In the b-tag
category the \ttbar background is larger than the \Wjets background.}
\label{fig:bkgs_highmtctrl}
\end{figure}

@@

The uncertainty in the luminosity measurement amounts to 6.2\% for

@@

using simulation.

@@

The combined uncertainty in the electron and muon identification, isolation, and
trigger efficiencies amounts to 2\%. For hadronic taus the identification and
isolation uncertainty amounts to 6\% per \Pgth in the \etau, \mutau and \tautau channels,
with an additional 7\% uncertainty
in the tau trigger efficiency added in quadrature for the \tautau channel. This
uncertainty is split between a part that is correlated between the channels and a
part that is not, The correlated part amounts to 

@@

The uncertainties on lepton and hadronic tau identification, isolation and 

@@

is estimated using simulation.

@@

The uncertainty in the $\text{jet}\rightarrow\Pgth$ fake rate

@@

to those backgrounds where the normalisation is estimated using simulation and
where the hadronic taus are faked by jets, that is the \Zellell background

@@

\subsubsection*{$\Pe\rightarrow\Pgth$ and $\Pgm\rightarrow\Pgth$ fake rates}
The $\Pe\rightarrow\Pgth$ fake rate uncertainty ranges from $10$--$30$\%

@@

applied to the \Zellell background in which the hadronic tau is faked by an electron.
The $\Pgm\rightarrow\Pgth$ fake rate uncertainty ranges from $20$--$30$\% depending
on the anti-muon discriminator used. This uncertainty is applied to the \Zellell
background in which the hadronic tau is faked by a muon.

@@

The uncertainty in the jet energy corrections is applied
by shifting the jet energy up and down by a \pT-and $\eta$-dependendent

@@

each category. The uncertainty ranges from $0$--$10$\% depending on process and category.

@@

Uncertainties in the b-tagging efficiency and light jet mis-tagging
rates are given as a function of jet \pT and $\eta$ for the 

@@

The b-tagging scale factors are varied within these uncertainties

@@

evaluated. The uncertainty varies from $0$--$5$\%.

@@

Uncertainties in the \MET~resolution and response are estimated

@@

uncertainties and evaluating the effect on process

@@

the Drell-Yan cross section uncertainty is not applied. In the no b-tag (b-tag) category a 3\% (5\%)
extrapolation uncertainty from the kinematic phase space of the \Zmm to the \Ztautau selection is applied.
\item \Zellell: The uncertainty in the Drell-Yan cross section
is 4\% \cite{fewz31}.
\item \ttbar: The uncertainty in the \ttbar production cross section amounts
to 6\% \cite{toppp}.
\item Di-boson and single-top: The combined uncertainty on the di-boson and
single-top production cross sections amounts to 5\% \cite{mcfm,hathor1,hathor2}.

@@

in the observed data and subtracted backgrounds in the control regions are taken into account by

@@

uncertainty in $R_{\PW}^{\text{OS/SS}}$ amounts to 2\% in the no b-tag

@@

category of the \mutau (\etau) channel. The systematic uncertainty in

@@

The statistical uncertainty in the low-\mT to high-\mT~ratio is 2\% in the no b-tag

@@

The systematic uncertainty in this ratio amounts to 20\%. As the \Wjets background
in the \tautau and \emu channels is estimated from simulation a 4\% theoretical
production cross section uncertainty is applied \cite{fewz31}.
\item QCD: In the \emu channel the uncertainty in the QCD estimate

@@

\tautau channel the statistical uncertainty in the QCD estimate is derived from

@@

category and 20\% in the b-tag category. An additional systematic uncertainty in the

@@

uncertainties in the observation and subtracted backgrounds in the control
regions used to derive the QCD estimate is accounted for by the inclusion of these control
regions in the fit. The uncertainty in the opposite-sign to same-sign ratio, based on

@@

uncertainties in the SM and MSSM Higgs cross section predictions are taken into account.

@@

\subsection{Shape uncertainties}
\label{sec:mssm_uncs_shape}
\subsubsection*{$\Pgt_{h}$ energy scale}
The energy of hadronic taus is varied up and down by 3\% \cite{CMS-PAS-HIG-16-037}, affecting
the shape of the total transverse mass distribution.
The uncertainty is applied to the signal samples and to
backgrounds containing real hadronic taus in the \etau, \mutau, and \tautau channels, namely
\Ztautau, and the components of the \ttbar and single-top+di-boson background with real 
hadronic taus.
\subsubsection*{Electron energy scale}
The energy of electrons is varied by 1\% in the barrel and by 2.5\% in the endcaps \cite{CMS-PAS-HIG-16-037}. This 
uncertainty is applied to the
signals and to the \Ztautau background in the \emu channel.
\subsubsection*{High-\pT~$\Pgth$ ID efficiency}
An additional $\Pgth$ identification uncertainty of $\frac{20\% \times p_{\text{T}}}{\TeV}$
is applied to account for the extrapolation from the tau ID efficiency
measurement, which uses mostly taus close to the \PZ peak, to taus with higher transverse momenta \cite{CMS-PAS-HIG-16-037}. This
uncertainty is applied to signal and backgrounds with real taus in the \etau, \mutau and \tautau channels.
The shape difference between the nominal, up- and down- shapes for this uncertainty in the no b-tag category
of the \tautau channel can be seen for a high-mass signal sample in figure \ref{fig:mssm_highpttauid_shapes}a and
for the \Ztautau background in figure \ref{fig:mssm_highpttauid_shapes}b. Because the \Ztautau background
has much softer hadronic taus than the high-mass signal sample, the impact of this uncertainty on the shape
is much smaller.
\begin{figure}[h!]
\begin{center}
\subfloat[$\Pg\Pg\phi$ signal at $m_{\phi} = 3.2\,\TeV$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/highpT_tauID_comp_tt_nobtag_ggh3200.pdf}}
\subfloat[\Ztautau background]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/highpT_tauID_comp_tt_nobtag_ZTT.pdf}}
\end{center}
\caption[Impact of the high-\pT~tau ID uncertainty in the no b-tag category
of the \tautau channel for a high-mass signal sample and the \Ztautau
background.]{Impact of the high-\pT~tau ID uncertainty in the no b-tag category of the
\tautau channel for (a) a high-mass signal sample and (b) the \Ztautau background. The effect on the shape is much
larger in the high-mass signal sample, which contains hadronically decaying taus with much higher
\pT~than the \Ztautau sample.}
\label{fig:mssm_highpttauid_shapes}
\end{figure}
\subsubsection*{Top quark \pT~reweighting}
To account for the uncertainty in the derivation of the top-quark \pT~reweighting, a shape
uncertainty is applied to the \ttbar background. This uncertainty amounts to a 100\% variation
of the correction, that is the difference between applying the correction twice and not applying the correction at all.
\subsubsection*{Drell-Yan shape reweighting}
An uncertainty in the Drell-Yan shape reweighting based on \Zmm events
is applied as 100\% of the correction to the \Ztautau background \cite{CMS-PAS-HIG-16-037}. 
\subsubsection*{Jet$\rightarrow\Pgt_{h}$ fake rate shape reweighting}
On the \Wjets background in the \etau and \mutau channels a shape 
uncertainty of $\frac{-20\% \times p_{\text{T}}}{\GeV}$ is 
applied. This uncertainty is derived from variations in the data/\ac{MC} ratio
for the $\text{jet}\rightarrow\Pgth$ fake rate as a function of jet \pT~in 
\Wjets events \cite{CMS-PAS-HIG-16-037}.

@@

\subsection{Inclusion of control regions in the fit}
\label{sec:mssm_sigext_ctrl}
The control regions used for estimation of the 
\Wjets and QCD background contributions in the signal regions
 are included in the fit. They
are added to the likelihood as single-bin counting experiments. In a given
category of one of the channels, the \Wjets
normalisation is fully correlated between the three control 
regions and the signal region. One common, freely floating, nuisance parameter
controls the \Wjets normalisation in all four regions. The QCD normalisation
is fully correlated between the opposite-sign and same-sign low-\mT~regions. The
same is true for the opposite-sign and same-sign high-\mT~regions. This means there are
two freely floating nuisance parameters that govern the QCD normalisation: one
that controls the QCD normalisation in the two low-\mT~regions, and one
that controls it in the two high-\mT~regions.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-a.pdf}}
\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_005-b.pdf}}
\end{center}
\caption[Distributions of \mTtot~in the no b-tag and b-tag categories
of the \mutau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
of the \mutau channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid. Note that, to incorporate
the observed Higgs boson at $125\,\GeV$, the $m_{\PHiggslight}^{\text{mod+}}$ scenario includes a \PHiggslight boson
at around $125\,\GeV$ with a much larger \xsbr than the $1\,\TeV$ \PHiggs and \PHiggsps, and this is
the reason for the doubly-peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_results_mttot_mt}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-a.pdf}}
\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_006-b.pdf}}
\end{center}
\caption[Distributions of \mTtot~inthe no b-tag and b-tag 
categories of the \etau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
of the \etau channel. The signal of the three neutral Higgs bosons at \mA~=$1\,\TeV$
and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
%the observed Higgs boson at 125 GeV, the $m_{h}^{\text{mod+}}$ scenario includes a h boson
%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_results_mttot_et}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-a.pdf}}
\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{MSSM/Figures/CMS-PAS-HIG-16-037_Figure_008-b.pdf}}
\end{center}
\caption[Distributions of \mTtot~in the no b-tag and b-tag categories
of the \tautau channel.]{Distributions of \mTtot~in the (a) no b-tag and (b) b-tag categories 
of the \tautau channel. The signal of the three neutral Higgs bosons at \mA~$=1\,\TeV$ 
and \tanb~$=50$ in the $m_{\PHiggslight}^{\text{mod+}}$ scenario is overlaid \cite{CMS-PAS-HIG-16-037}.}% Note that, to incorporate
%the observed Higgs boson at 125 GeV, the $m_{h}^{mod+}$ scenario includes a h boson
%at around 125 GeV with a much larger $\sigma \times$BR than the 1 TeV H and A, and this is
%the reason for the doubly--peaking shape of the overlaid signal \cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_results_mttot_tt}
\end{figure}
